### 2023-04-11 main.tex
i

In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These boundaries, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are

@@

The action of $\mathcal{H}$ amounts to the permutation of the two sites, i.e.

@@

		\alpha_{1}-1&\alpha_{1}&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\ldots&\alpha_{2}\\
		\vdots&\vdots&\vdots&\vdots\\
		\alpha_{N}&\alpha_{N}&\ldots&\alpha_{N}-1

@@

		\beta_{1}-1&\beta_{1}&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\ldots&\beta_{2}\\
		\vdots&\vdots&\vdots&\vdots\\
		\beta_{N}&\beta_{N}&\ldots&\beta_{N}-1

@@

In this setting the extra-sites are denoted by $0$ and $L+1$, since connected with sites $1$ and $L$ of the chain respectively. Moreover, the matrix $R_{x}$ reduces to the identity. Therefore, the duality matrix reads as
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{E^{x}}\otimes \mathcal{D}_{L+1}

@@

	\widetilde{H}=H_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{L+1}
with the operators \eqref{edgeHamiltonian} and \eqref{siteDualHamiltonian}. In the long-time horizon, the dual process voids the chain, and all particles are eventually absorbed at extra-site $0$ or $L+1$. \\
Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product ansatz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat2017exact}). 
 Calling $|{P}(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 

@@

\textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them 

@@

As pointed already pointed out, the MPA gives an abstract form of the steady state, in terms of an algebra of operators. However, to write explicitly the steady state one should know a representation of this algebra. Another approach is to directly use the commutators and figure out correlations from them. This path has been followed in \cite{vanicat2017exact} to compute one and two points correlations. However, it is interesting to put effort in this direction and look for explicit form of arbitrary correlations. We will carry out this aim by the use of duality, proved in Section \ref{sectionDuality}. The idea is summarized in the following. We define a sequence of similarity transformation such that 

@@

where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$. The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix. Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. This informally explains the role of duality. The second transformation $\mathcal{S}_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs. \\
This idea is exposed as follows. We first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators. Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.

\begin{comment}
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\end{comment}
\subsubsection{The similarity transformation}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
\end{equation}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
\begin{equation}
    \mathcal{S}_{1}=S_{1}^{\otimes L}
\end{equation}
that is related with the duality matrix by 
\begin{equation}
\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
\end{equation}
 This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
\end{equation}
that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
\end{equation}
The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
\begin{equation}
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
\end{equation}
Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
\begin{equation}
	H^{'}|\Psi^{'}\rangle=0
\end{equation}
therefore, it is easy to see that 
\begin{equation}\label{S1-Inverse}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
\end{equation}

@@

The boundary Hamiltonians are the following 

@@

We obtain the new operators of the MPA that by transforming the original one by $S$

@@

We can also reverse the transformation by $S^{-1}$ and get back: 

@@

The vector $|\Psi^{''}\rangle$ is written as:

@@

	|Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

such that for each site $x\in \{1,\ldots,L\}$ $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 

@@

We  rewrite \eqref{commutationsBula} as:

@@

By taking the product over the sites $i$ from $1$ to L we obtain 

@@

where $s_i=\sum_{a=1}^N\delta_{n_k^i,1}$. Finally we take the tensor product of the vectors $|s_{x}\rangle$ and we obtain
	|\mathbf{s}\rangle=\bigotimes_{i=1}^{L}|s_{x}\rangle=|\mathbf{s}\rangle
with $s_{x}\in\{1,\ldots,N\}$. For a fixed site $i$, because of the hard-core interaction that allows at most one particle on type different from $1$ ,at site $i$ we have 

@@

Finally summing over all $\mathbf{s}\in \Omega$ (that is equivalent, $\forall i\in\{1,\ldots,L\}$, to summing over all the possible values of each $s_{x}\in\{1,\ldots,N\}$) we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}.

@@

			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}

@@

	c_{x}=\begin{cases}
		1\quad \text{if}\quad s_{x}\neq 1\\
		0\quad \text{if}\quad s_{x}=1
	\end{cases}\qquad \forall x\in \{1,\ldots,L\}

@@

    e_{ab}=e_{a}^{b}=\left(\delta_{a,c}\delta_{b,d}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,\}

@@

    \begin{equation}\label{InverseS2}
    	\begin{split}
    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    		\right. \\&+ \left. 
    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
    	\end{split}
    \end{equation}
    We prove it by induction. When $L=1$ it is true, indeed
    \begin{equation}
    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    \end{equation}
    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
\begin{align*}
    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    	\\&=
    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
    	\\&=
    	\left(S_{2}^{\otimes L+1}\right)^{-1}
\end{align*}
    \begin{comment}

>>>>

In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These boundaries, exchanging particle with the external environment, by putting the chain out of equilibrium. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are

@@

The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.

@@

		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1

@@

		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1

@@

Under these assumption the Hamiltonian is integrable. \\
For what concerns duality, in this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain. Moreover, the matrix $R_{x}$ reduces to the identity. Therefore, the duality matrix reads as
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{(E^{x})}\otimes \mathcal{D}_{L+1}

@@

	\widetilde{H}=\widetilde{H}_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+\widetilde{H}_{L+1}
In the long-time horizon, the dual process voids the chain, and all particles are eventually absorbed at extra-site $0$ or $L+1$.
\paragraph{Matrix Product Ansatz (MPA)} Matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we recall its main points.\\
 Calling $|\Psi(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 

@@

\textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$:

@@

The MPA gives an abstract form of the steady state in terms of an algebra of operators. However, to write explicitly the steady state one should know a representation of this algebra. Another approach is to directly use the commutators and figure out correlations from them. This path has been followed in \cite{vanicat2017exact} to compute one and two points correlations. However, it is interesting to put effort in this direction and look for explicit form of arbitrary correlations. We will carry out this aim by the use of duality, proved in Section \ref{sectionDuality}. The idea is summarized in the following. We define a sequence of similarity transformation such that 

@@

where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$.\\
The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix. Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. This informally explains the role of duality. The second transformation $\mathcal{S}_{2}$ diagonalize the right boundary. This allows to simplify a lot the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs. \\
The computation are organized as follows: we first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators. Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\subsubsection{The similarity transformation}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
    \mathcal{S}_{1}=S_{1}^{\otimes L}
that is related with the duality matrix by 
\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
 This $\mathcal{S}_{1}$ is invertible, then we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
The boundary Hamiltonians$B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
	H^{'}|\Psi^{'}\rangle=0
then, it is easy to see that 
\begin{equation}\label{S1-Inverse}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle

@@

The boundary Hamiltonians of $H^{''}$ reads

@@

We obtain 

@@

and, we can also reverse the transformation by $S^{-1}$ and get back: 

@@

Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ is written as:

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 

@@

We have

@@

By taking the product over the sites $x$ from $1$ to $L$ we obtain 

@@

where $s_{x}=\sum_{a=1}^N\delta_{n_{k}^{x},1}$. Finally we take the tensor product of the vectors $|s_{x}\rangle$ and we obtain
	|\mathbf{s}\rangle=\bigotimes_{x=1}^{L}|s_{x}\rangle=|\mathbf{s}\rangle
with $s_{x}\in\{1,\ldots,N\}$. For a fixed site $x$, because of the hard-core interaction that allows at most one particle on type different from $1$, we have 

@@

Finally summing over all $\mathbf{s}\in \Omega$  we obtain \eqref{ResulsBasis}.

@@

			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{l}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}

@@

	c_{y}=\begin{cases}
		1\quad \text{if}\quad s_{y}\neq 1\\
		0\quad \text{if}\quad s_{y}=1
	\end{cases}\qquad \forall y\in \{1,\ldots,L\}

@@

    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,\}

@@

    \begin{equation}\label{InverseS2}
    	\begin{split}
    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    		\right. \\&+ \left. 
    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
    	\end{split}
    \end{equation}
    We prove it by induction. When $L=1$ it is true, indeed
    \begin{equation}
    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    \end{equation}
    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
\begin{align*}
    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
    	\\&=
    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
    	\\&=
    	\left(S_{2}^{\otimes L+1}\right)^{-1}
\end{align*}
    \begin{comment}
